Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences

### 2020-01-06 draft.tex
new tau

% In the code, called Current solution
We also define the \strat{Extreme completions} strategy, which we consider as a more realistic baseline. 
Consider the solution of the minimax regret game, 
 $(x^{*},\bar{y},\bar{\profile},\bar{\w})$, where $x^{*}$ is the minimax regret optimal alternative, and $\bar{y} = \arg \max_{y \in A} \PMR(x,y; \pprofile, W)$, $\bar{\profile}$ and $\bar{\w}$ are the adversarial choices, thus, the instantiations that, given the choice of $x^*$, maximize the regret. 
Define: 
\begin{align}
\tau_{1} & = \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w),  \label{eq:tau1} \\
\tau_{2} & = \min_{\profile \in C(\pprofile)} s(\bar{y},\profile, \bar{\w}) -  s(x^{*}; \profile, \bar{\w}).
\end{align}
Intuitively the quantity $\MMR - \tau_{1} = \max_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w) - \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$ estimates the contribution to regret of our uncertainty about the weights $\w$, while $\MMR - \tau_{2} $ estimates the uncertainty about the profile.
Therefore, whenever $\tau_{1} < \tau_{2}$ we ask a question to the chair, and compare componentwise $\bar{\w}$ and $\w^{\tau}$, the argmax of Eq. (\ref{eq:tau1}), to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
Instead, if $\tau_{1} > \tau_{2}$ we ask a question to one of the agents. We select the question by checking for each agent $j$ the difference between the difference of the ranks of $x$ and $y$ in the profile that minimizes compared to the one that maximizes the difference of scores, and pick an agent related to the highest difference, then pick $x$ or $y$ with $1/2$ chances as the first alternative of the question, and pick an incomparable alternative equiprobably as the second one.

>>>>

% In the code, called Current solution
We also define the \strat{Extreme completions} strategy, which we consider as a more realistic baseline. 
Consider the solution of the minimax regret game, 
 $(x^{*},\bar{y},\bar{\profile},\bar{\w})$, where $x^{*}$ is the minimax regret optimal alternative, and $\bar{y} = \arg \max_{y \in A} \PMR(x,y; \pprofile, W)$, $\bar{\profile}$ and $\bar{\w}$ are the adversarial choices, thus, the instantiations that, given the choice of $x^*$, maximize the regret. 
Define: 
\begin{align}
\tau_{1} & = \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w),  \label{eq:tau1} \\
\tau_{2} & = \min_{\profile \in C(\pprofile)} s(\bar{y},\profile, \bar{\w}) -  s(x^{*}; \profile, \bar{\w}).
\end{align}
{\color{red}
\begin{align}
	\tau_{\w} & = \min_{\w \in W} s^{\bar{\profile},\w}(\bar{y}) - s^{\bar{\profile},\w}(x^{*}) \\
	\tau_{\profile_i} & = \min_{\hat{\profile_i} \in C(\pprofile)} s^{\hat{\profile_i},\bar{\w}}(\bar{y}) -  s^{\hat{\profile_i},\bar{\w}}(x^{*}) 
\end{align}
where $\hat{\profile_i}$ is defined as $\bar{\profile}$ except for $i$, $\forall i \in \{1, \dots, n\}$. }

Intuitively the quantity $\MMR - \tau_{1} = \max_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w) - \min_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$ estimates the contribution to regret of our uncertainty about the weights $\w$, while $\MMR - \tau_{2} $ estimates the uncertainty about the profile.
Therefore, whenever $\tau_{1} < \tau_{2}$ we ask a question to the chair, and compare component-wise $\bar{\w}$ and $\w^{\tau}$, the argmax of Eq. (\ref{eq:tau1}), to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
Instead, if $\tau_{1} > \tau_{2}$ we ask a question to one of the agents. We select the question by checking for each agent $j$ the difference between the difference of the ranks of $x$ and $y$ in the profile that minimizes compared to the one that maximizes the difference of scores, and pick an agent related to the highest difference, then pick $x$ or $y$ with $1/2$ chances as the first alternative of the question, and pick an incomparable alternative equiprobably as the second one.
